---
title: "Analysis and Sentiment Analysis"
author: "Espadon, Bernasol, Gerona"
output: pdf_document
---
Data Cleaning
```{r}
library(dplyr)
library(stringr)
```


```{r}
tweets_df <- read.csv("/cloud/project/Analysis and Sentiment Analysis/tweetsDF.csv")
```

```{r}
# Remove duplicates
tweets_df <- tweets_df %>%
  distinct()

```


```{r}
missing_values <- colSums(is.na(tweets_df))
```


```{r}
write.csv(tweets_df, "cleaned_tweets.csv", row.names = FALSE)
```

```{r}
tweets_df$text <- tweets_df$text %>%
str_replace_all("http\\S+|www\\.\\S+", "") %>%
str_replace_all("[^[:alnum:][:space:]]", "") %>%
str_squish()
```


```{r}
print(head(tweets_df))
```


```{r}
library(dplyr)
library(ggplot2)
library(lubridate)
```

```{r}
tweets_df$created <- ymd_hms(tweets_df$created)
```


```{r}
daily_trend <- tweets_df %>%
mutate(date = as_date(created)) %>%
group_by(date) %>%
summarise(tweet_count = n())
```

```{r}
ggplot(daily_trend, aes(x = date, y = tweet_count)) +
geom_line(color = "blue", size = 1) +
labs(
title = "Daily Tweet Trend",
x = "Date",
y = "Number of Tweets"
) +
theme_minimal()
```



Sentimental Analysis


```{r}
library(dplyr)
library(tidytext)
library(ggplot2)
```

```{r}
bing_lexicon <- get_sentiments("bing")
```

```{r}
tokenized_tweets <- tweets_df %>%
unnest_tokens(word, text) %>%
anti_join(stop_words)
```

```{r}
sentiment_analysis <- tokenized_tweets %>%
inner_join(bing_lexicon, by = "word") %>%
count(sentiment) %>%
mutate(percent = n / sum(n) * 100)
```

```{r}
ggplot(sentiment_analysis, aes(x = sentiment, y = percent, fill = sentiment)) +
geom_bar(stat = "identity") +
labs(
title = "Sentiment Analysis of Tweets",
x = "Sentiment",
y = "Percentage of Words"
) +
theme_minimal()
```



2.Present your Use Case on what you will do with the dataset.
Use Case: Tracking Public Opinion on Social Issues
This project involves analyzing a dataset of 58,085 tweets to understand shifts in public opinion, engagement trends, and emotional responses to events. By examining tweet content, timestamps, and sources (e.g., Android/iOS), we aim to identify patterns over time.
The findings will benefit governments, brands, media outlets, and social movements by offering actionable insights into public reactions, helping refine strategies, and guiding decision-making. Key deliverables include visualizations of trends, sentiment distributions (positive, neutral, negative), and analyses linking sentiment changes to significant events. These insights can help stakeholders anticipate future trends and respond effectively.


3.Make sure to describe each graph you have created. Give insights.

3. Graph Descriptions and Insights
Trend Analysis: Daily Tweet Count
Graph Description:

Type: Line graph
X-axis: Date
Y-axis: Number of Tweets
Purpose: This graph illustrates daily tweet counts over a specific period, highlighting fluctuations in tweet activity. It helps pinpoint spikes or dips that may correspond to notable events or significant moments.
Insights:

Spike in Activity: Days with sudden increases in tweet counts could indicate major events or viral moments that drove heightened engagement.
Trends Over Time: Consistent high activity (e.g., weekends or specific days) or spikes tied to events reveal patterns in public engagement.
Overall Volume: Steady tweet counts suggest sustained interest in the topic, while significant fluctuations indicate that public interest may be event-driven.



Sentiment Analysis: Sentiment Distribution (Positive, Negative, Neutral)
Graph Description:

Type: Bar chart
X-axis: Sentiment categories (Positive, Negative, Neutral)
Y-axis: Percentage of Words
Purpose: This chart presents the proportions of words in tweets categorized by sentiment, offering insights into the emotional tone of public discourse.
Insights:

Dominant Sentiment: A high prevalence of one sentiment (e.g., negative) indicates a strong emotional reaction from the public toward the topic or event.
Sentiment Balance: A balanced distribution across positive, negative, and neutral sentiments suggests a more nuanced or mixed public response.
Sentiment Shifts: Comparing sentiment distributions across different timeframes (e.g., before and after a significant event) can reveal changes in public opinion.
